---
title: "Carotid Sim Trial Consistency"
author: "Guillaume Kugener"
date: "4/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/carotid_model/preprocess_data.R')

plot_dir <- file.path(source_dir, 'plots')
```

## General demographics figure

## Compare sites

```{r}
# Look at success rate across sites
compare_sites_data <- raw_data %>% 
  # dplyr::select(
  #   SurveyID, Group, Source, 
  #   `Start Date`,
  #   `Trial 1 Success`, `Trial 2 Success`,
  #   `Trial 1 TTH`, `Trial 2 TTH`,
  #   `trial 1 ebl`, `trial 2 ebl`
  # ) %>%
  mutate(dd=format(as.Date(`Start Date`), format='%Y-%m')) %>%
  mutate(SiteGroup=ifelse(is.na(dd), Source, paste0(Source, '_', dd))) %>%
  mutate(SiteGroup2=case_when(
    Source == 'Emory' ~ 'Emory',
    grepl('[0-9][0-9]$', SurveyID) ~ paste0('USC', gsub('[0-9][0-9]$', '', SurveyID)),
    SurveyID %in% c('314c', '320b') ~ 'USC3', 
    TRUE ~ 'None'
  )) %>% 
  mutate(SiteGroup2=gsub('USCUSC1', 'USC120+', SiteGroup2))
```

```{r}
# plot demographics by site
confidence_values <- compare_sites_data %>%
  dplyr::select(SurveyID, Group, SiteGroup2, generalconfidencepre, generalconfidencepost, carotidconfidencepre, carotidconfidencepost) %>%
  gather(conf_var, conf_val, -SurveyID, -Group, -SiteGroup2) %>%
  mutate(conf_var=factor(conf_var, levels=c('generalconfidencepre', 'generalconfidencepost', 'carotidconfidencepre', 'carotidconfidencepost')))

ggplot(confidence_values, aes(conf_var, conf_val, color=SiteGroup2)) +
  geom_boxplot(alpha=0.5)
  # geom_sina() +
  # geom_violin()
  # stat_compare_means(label = "p.signif", paired = T, na.rm = T)

conf_tile_plot <- confidence_values %>%
  filter(!is.na(conf_val)) %>%
  group_by(SiteGroup2, conf_var, conf_val) %>% 
  dplyr::summarise(count=n()) %>%
  mutate(count=ifelse(is.na(count), 0, count)) %>%
  group_by(SiteGroup2, conf_var) %>%
  mutate(total=sum(count))

ggplot(conf_tile_plot, aes(SiteGroup2, conf_val, fill=count/total)) +
  # geom_boxplot(alpha=0.5) +
  scale_fill_gradient(low='white', high='red') +
  geom_tile() +
  facet_wrap(~conf_var, nrow=1) + 
  theme(panel.background=element_rect(fill="white", colour="black"))

confidence_across_sites <- ggplot(conf_tile_plot, aes(SiteGroup2, count/total, fill=conf_val)) +
  geom_bar(stat='identity') +
  scale_fill_gradient2(low='blue', high='red', mid='white', midpoint=3) +
  facet_wrap(~conf_var, ncol=2)

ggsave(confidence_across_sites, filename = file.path(plot_dir, 'confidence_across_sites.png'), width=8, height=5)
```

```{r}
aov(`Trial 1 Success` ~ SiteGroup2, data = compare_sites_data %>% filter(Group=='Attending')) %>% summary()
aov(`Trial 1 TTH` ~ SiteGroup2, data = compare_sites_data %>% filter(Group=='Attending')) %>% summary()
aov(`trial 1 ebl` ~ SiteGroup2, data = compare_sites_data %>% filter(Group=='Attending')) %>% summary()
```

```{r}
ggplot(compare_sites_data, aes(SiteGroup2, `Trial 1 TTH`)) +
  geom_boxplot() +
  facet_wrap(~Group, ncol = 1)

trial_success_by_site <- compare_sites_data %>%
  mutate(T1S=case_when(
      `Trial 1 Success`==0 ~ 'Fail', 
      `Trial 1 Success`==1 ~ 'Success',
      TRUE ~ 'None'),
    T2S=case_when(
      `Trial 2 Success`==0 ~ 'Fail', 
      `Trial 2 Success`==1 ~ 'Success',
      TRUE ~ 'None')
  ) %>%
  dplyr::select(SurveyID, Group, Source, SiteGroup2, T1S, T2S) %>%
  gather(trial, value, -SurveyID, -Group, -Source, -SiteGroup2) %>%
  filter(value != 'None') %>%
  group_by(SiteGroup2, trial, value) %>%
  dplyr::summarise(count=n()) %>%
  group_by(SiteGroup2, trial) %>%
  mutate(total=sum(count))

# Add p values between all groups
# Need to do a fishers between all of them
fisher_sites_ps <- NULL
for (si in unique(trial_success_by_site$SiteGroup2)) {
  contig_table_sites <- trial_success_by_site %>% 
    filter(SiteGroup2 == si) %>%
    reshape2::dcast(trial ~ value, value.var='count') %>%
    column_to_rownames(var = 'trial')
  contig_table_sites[is.na(contig_table_sites)] <- 0
  fisher_sites_ps %<>% rbind(data.frame(SiteGroup2=si, p=fisher.test(contig_table_sites)$p.value, stringsAsFactors = F))
}

fisher_sites_ps %<>% 
  mutate(p_text=ifelse(p < 0.05, paste0('p=', round(p, 3)), 'ns')) %>% 
  mutate(trial=NA)

success_rate_with_ps <- ggplot(trial_success_by_site %>% filter(value=='Success'), aes(SiteGroup2, count/total*100, fill=trial)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(data = fisher_sites_ps %>% mutate(y=105), aes(SiteGroup2, y, label = p_text)) +
  ylab('Success rate') +
  xlab('Site')

ggsave(success_rate_with_ps, filename = file.path(plot_dir, 'success_rate_by_site.png'), width = 8, height = 5, device = 'png')

success_rate_with_ps

success_counts_with_ps <- ggplot(trial_success_by_site %>% filter(value=='Success'), aes(SiteGroup2, count, fill=trial)) +
  # geom_bar(aes(SiteGroup2, total), stat = 'identity', position = position_dodge(), color='grey', alpha=0.5) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(data = fisher_sites_ps %>% mutate(y=35), aes(SiteGroup2, y, label = p_text)) +
  ylab('Number successful trials') +
  xlab('Site')

ggsave(success_counts_with_ps, filename = file.path(plot_dir, 'success_counts_by_site.png'), width = 8, height = 5, device = 'png')

success_counts_with_ps
```

```{r}
trial_tth_by_site <- compare_sites_data %>%
  mutate(T1S=case_when(
      `Trial 1 Success`==0 ~ 'Fail', 
      `Trial 1 Success`==1 ~ 'Success',
      TRUE ~ 'None'),
    T2S=case_when(
      `Trial 2 Success`==0 ~ 'Fail', 
      `Trial 2 Success`==1 ~ 'Success',
      TRUE ~ 'None')
  ) %>%
  dplyr::select(SurveyID, Group, Source, SiteGroup2, `Trial 1 TTH`, `Trial 2 TTH`) %>%
  filter(!is.na( `Trial 2 TTH`)) %>%
  gather(trial, value, -SurveyID, -Group, -Source, -SiteGroup2)

tth_by_site_final <- ggplot(trial_tth_by_site, aes(SiteGroup2, value, color=trial)) +
  geom_boxplot(fill='grey', alpha=0.5, outlier.shape=NA) +
  # geom_point(position = position_jitterdodge()) +
  geom_sina() +
  stat_compare_means(aes(group = trial), label = "p.signif", paired = T) +
  ylab('TTH') + xlab('Site')

tth_by_site_final

ggsave(tth_by_site_final, filename = file.path(plot_dir, 'tth_by_site_final.png'), width = 8, height = 5)
```

```{r}
trial_ebl_by_site <- compare_sites_data %>%
  mutate(T1S=case_when(
      `Trial 1 Success`==0 ~ 'Fail', 
      `Trial 1 Success`==1 ~ 'Success',
      TRUE ~ 'None'),
    T2S=case_when(
      `Trial 2 Success`==0 ~ 'Fail', 
      `Trial 2 Success`==1 ~ 'Success',
      TRUE ~ 'None')
  ) %>%
  dplyr::select(SurveyID, Group, Source, SiteGroup2, `trial 1 ebl`, `trial 2 ebl`) %>%
  filter(!is.na( `trial 2 ebl`)) %>%
  gather(trial, value, -SurveyID, -Group, -Source, -SiteGroup2)

ebl_by_site_final <- ggplot(trial_ebl_by_site, aes(SiteGroup2, value, color=trial)) +
  geom_boxplot(fill='grey', alpha=0.5, outlier.shape=NA) +
  # geom_point(position = position_jitterdodge()) +
  geom_sina() +
  stat_compare_means(aes(group = trial), label = "p.signif", paired = T) +
  ylab('EBL') + xlab('Site')

ebl_by_site_final

ggsave(ebl_by_site_final, filename = file.path(plot_dir, 'ebl_by_site_final.png'), width = 8, height = 5)
```

```{r eval=FALSE}
attendings_trial_across_sites <- ggplot(trial_success_by_site %>% 
         filter(T1S=='Success', Group=='Attending') %>% 
         group_by(SiteGroup2) %>% 
         dplyr::summarise(co=sum(count)/sum(total)*100), 
       aes(SiteGroup2, co)) +
  geom_bar(stat = 'identity') +
  ylab('Percent success trial 1 (attendings only)') +
  scale_y_continuous(limits = c(0, 100))

ggsave(attendings_trial_across_sites, filename=file.path(plot_dir, 'success_across_sites.png'), width = 8, height = 5, device = 'png')
```

## Attending trial 1 vs. trainee trial 2.

We want to see how comparable these are. Are trainees with some training able to perform just as well as attendings with no training?

```{r}
a1_t2_data <- raw_data %>%
  dplyr::select(
    SurveyID, Group, Source, 
     `Trial 1 Success`, `Trial 2 Success`,
    `Trial 1 TTH`, `Trial 2 TTH`,
    `trial 1 ebl`, `trial 2 ebl`
  ) %>%
  gather(var, value, -SurveyID, -Group, -Source) %>%
  mutate(
    trial=as.numeric(stringr::str_extract(pattern='[0-9]+', string=var)),
    variable = stringr::str_extract(pattern='ebl|TTH|Success', string=var)
  ) %>%
  filter((Group=='Trainee' & trial == 2) | (Group == 'Attending' & trial == 1)) %>%
  reshape2::dcast(SurveyID + Group + Source + trial ~ variable, value.var='value')
```

```{r}
# Compare success 
compare_success_a1_t2 <- a1_t2_data %>%
  dplyr::select(SurveyID, Group, trial, Success) %>%
  filter(!is.na(Success)) %>%
  group_by(Group, Success) %>%
  dplyr::summarise(count=n()) %>%
  mutate(Success==case_when(
      Success==0 ~ 'Fail', 
      Success==1 ~ 'Success',
      TRUE ~ 'None')
  ) %>%
  reshape2::dcast(Group ~ Success, value.var='count')

# Looks like trainees on trial 2 are actually better than attendings on trial 1 -> this supports the point
compare_success_a1_t2 %>%
  column_to_rownames(var='Group') %>%
  fisher.test()

compare_success_a1_t2_plot <- a1_t2_data %>%
  mutate(G2=paste0(Group, ', Trial ', trial)) %>%
  group_by(G2) %>%
  dplyr::summarise(count=n(), succeeded=sum(Success))

a1_t2_plot <- ggplot(compare_success_a1_t2_plot, aes(G2, succeeded/count*100)) +
  geom_bar(stat='identity', color='black', alpha=0.5, fill='grey') +
  ylab('Success rate') +
  scale_y_continuous(expand=c(0,0), limits=c(0, 105))

a1_t2_plot

ggsave(a1_t2_plot, filename = file.path(plot_dir, 'success_attending_t1_vs_trainee_t2.png'), width = 8, height = 5)
```

```{r}
## Trainees are better in trial 2 than attendings in trial 1 when using TTH as mesaurement. No significant change when using EBL
t.test(
  a1_t2_data %>% filter(Group=='Trainee') %$% ebl,
  a1_t2_data %>% filter(Group=='Attending') %$% ebl,
  paired = F
)

tth_a1_t2_plot <- ggplot(a1_t2_data, aes(Group, TTH)) +
  geom_boxplot(color='black', alpha=0.5, fill='grey') +
  ylab('TTH')

ggsave(tth_a1_t2_plot, filename = file.path(plot_dir, 'tth_attending_t1_vs_trainee_t2.png'), width = 8, height = 5)

ebl_a1_t2_plot <- ggplot(a1_t2_data, aes(Group, ebl)) +
  geom_boxplot(color='black', alpha=0.5, fill='grey') +
  ylab('EBL')

ggsave(ebl_a1_t2_plot, filename = file.path(plot_dir, 'ebl_attending_t1_vs_trainee_t2.png'), width = 8, height = 5)
```

## Endoscopic cases over last year vs. perfromance (TTH, EBL, trial success). 

Look in all and only attendings.

```{r}
endolast12mo_data <- raw_data %>% 
  dplyr::select(
    SurveyID, Group, Source, 
    `Trial 1 Success`, `Trial 2 Success`,
    `Trial 1 TTH`, `Trial 2 TTH`,
    `trial 1 ebl`, `trial 2 ebl`,
    endolast12mo
  ) %>% filter(!is.na(endolast12mo)) %>%
  mutate(
    T1S=case_when(
      `Trial 1 Success`==0 ~ 'Fail', 
      `Trial 1 Success`==1 ~ 'Success',
      TRUE ~ 'None'),
    T2S=case_when(
      `Trial 2 Success`==0 ~ 'Fail', 
      `Trial 2 Success`==1 ~ 'Success',
      TRUE ~ 'None')
  )
```

```{r}
t1s_endo_t_val_plot <- t.test(
  endolast12mo_data %>% filter(T1S=='Fail') %$% endolast12mo,
  endolast12mo_data %>% filter(T1S=='Success') %$% endolast12mo,
  paired = F
)$p.value

ggplot(endolast12mo_data, aes(T1S, (endolast12mo))) +
  geom_boxplot() +
  xlab('Trial 1 success') +
  ylab('Endoscopic cases last 12 months') +
  annotate(geom = 'text', x=2, y = 200, label=paste0('p=', round(t1s_endo_t_val_plot, 2)))
```

```{r}
t2s_endo_t_val_plot <- t.test(
  endolast12mo_data %>% filter(T2S=='Fail') %$% endolast12mo,
  endolast12mo_data %>% filter(T2S=='Success') %$% endolast12mo,
  paired = F
)$p.value

ggplot(endolast12mo_data %>% filter(!is.na(T2S)), aes(T2S, (endolast12mo))) +
  geom_boxplot() +
  xlab('Trial 2 success') +
  ylab('Endoscopic cases last 12 months') +
  annotate(geom = 'text', x=2, y = 200, label=paste0('p=', round(t2s_endo_t_val_plot, 2)))
```
Same as above but now looking in attendings only

```{r}
attending_t1s_endo_t_val_plot <- t.test(
  endolast12mo_data %>% filter(Group=='Attending', T1S=='Fail') %$% endolast12mo,
  endolast12mo_data %>% filter(Group=='Attending', T1S=='Success') %$% endolast12mo,
  paired = F
)$p.value

ggplot(endolast12mo_data %>% filter(Group=='Attending'), aes(T1S, (endolast12mo))) +
  geom_boxplot() +
  xlab('Trial 1 success') +
  ylab('Endoscopic cases last 12 months') +
  annotate(geom = 'text', x=2, y = 200, label=paste0('p=', round(attending_t1s_endo_t_val_plot, 2)))
```

```{r}
attending_t2s_endo_t_val_plot <- t.test(
  endolast12mo_data %>% filter(Group=='Attending', T2S=='Fail') %$% endolast12mo,
  endolast12mo_data %>% filter(Group=='Attending', T2S=='Success') %$% endolast12mo,
  paired = F
)$p.value

ggplot(endolast12mo_data %>% filter(!is.na(T2S), Group=='Attending'), aes(T2S, (endolast12mo))) +
  geom_boxplot() +
  xlab('Trial 2 success') +
  ylab('Endoscopic cases last 12 months') +
  annotate(geom = 'text', x=2, y = 200, label=paste0('p=', round(attending_t2s_endo_t_val_plot, 2)))
```

## Length of training vs. success rate

```{r}
attendings_with_training_years <- raw_data %>%
    dplyr::select(
    SurveyID, Group, Source, 
    `Trial 1 Success`, `Trial 2 Success`,
    `Trial 1 TTH`, `Trial 2 TTH`,
    `trial 1 ebl`, `trial 2 ebl`,
    endolast12mo, Totyears, Attyears, Resyears
  ) %>% filter(Group=='Attending', !is.na(Totyears) | !is.na(Attyears) | !is.na(Resyears)) %>%
  # For Emory, I think total years for attendings is attyears in the main dataset
  mutate(Attyears=ifelse(Source=='Emory', Totyears, Attyears)) %>%
  filter(!is.na(Attyears)) %>%
  mutate(
    T1S=case_when(
      `Trial 1 Success`==0 ~ 'Fail', 
      `Trial 1 Success`==1 ~ 'Success',
      TRUE ~ 'None'),
    T2S=case_when(
      `Trial 2 Success`==0 ~ 'Fail', 
      `Trial 2 Success`==1 ~ 'Success',
      TRUE ~ 'None')
  )
```

```{r}
attending_t1s_years_t_val_plot <- t.test(
  attendings_with_training_years %>% filter(Group=='Attending', T1S=='Fail') %$% Attyears,
  attendings_with_training_years %>% filter(Group=='Attending', T1S=='Success') %$% Attyears,
  paired = F
)$p.value

ggplot(attendings_with_training_years, aes(T1S, Attyears)) +
  geom_boxplot() +
  xlab('Trial 1 success') +
  ylab('Years as an attending') +
  annotate(geom = 'text', x=2, y = 40, label=paste0('p=', round(attending_t1s_years_t_val_plot, 2)))
```

```{r}
attending_t2s_years_t_val_plot <- t.test(
  attendings_with_training_years %>% filter(Group=='Attending', T2S=='Fail') %$% Attyears,
  attendings_with_training_years %>% filter(Group=='Attending', T2S=='Success') %$% Attyears,
  paired = F
)$p.value

ggplot(attendings_with_training_years %>% filter(!is.na(T2S)), aes(T2S, Attyears)) +
  geom_boxplot() +
  xlab('Trial 2 success') +
  ylab('Years as an attending') +
  annotate(geom = 'text', x=2, y = 40, label=paste0('p=', round(attending_t2s_years_t_val_plot, 2)))
```









