---
title: "Cohort Characterization with APMs"
author: "Guillaume Kugener"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(magrittr)
library(ggrepel)
library(reshape2)
library(DT)
```

```{r}
plot_dir <- '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/'
```

# Cohort Characterization with APMs

In a previous manuscript, we characterized similarities and differences in the demographics of participants as they managed an ICA injury simulation. In this document, we want to characterize differences in successful and unsuccessful trials using APMs dervied from the videos. Specifically, these APMs are derived from annotations of these videos at 1 fps.

```{r include=FALSE}
# Frame dimensions
frame_dimensions <- read_csv('~/Documents/USC/USC_docs/ml/datasets/fps-1-uncropped/image_sizes.csv')

dimensions_grouping <- frame_dimensions %>%
  mutate(gname=paste0(w, 'x', h))

dg1920x1080 <- dimensions_grouping %>% filter(gname=='1920x1080') %$% trial_id
dg1280x720 <- dimensions_grouping %>% filter(gname=='1280x720') %$% trial_id
```

```{r include=FALSE}
# Load ground truth 1 fps data
gt_fps1 <- read_csv('~/Documents/USC/USC_docs/ml/datasets/fps-1-uncropped/ImageSets/Main/retinanet_surgical_1fps_complete.csv',
  col_names = c('file', 'x1', 'y1', 'x2', 'y2', 'tool')) %>%
  mutate(short_file_name=gsub('.*/', '', file)) %>%
  mutate(trial_id=gsub('[a-z]?_.*', '', short_file_name)) %>%
  mutate(frame=as.numeric(stringr::str_extract(pattern='[0-9]+', string=gsub('.*_', '', short_file_name))))

# batching_corrections <- gt_fps1 %>%
  # group_by()

# xs_mean <- mean(c(gt_fps1$x1, gt_fps1$x2), na.rm = T)
# xs_sd <- sd(c(gt_fps1$x1, gt_fps1$x2), na.rm = T)
# ys_mean <- mean(c(gt_fps1$y1, gt_fps1$y2), na.rm = T)
# ys_sd <- sd(c(gt_fps1$y1, gt_fps1$y2), na.rm = T)

gt_fps1 %<>%
  mutate(res=case_when(
    trial_id %in% dg1280x720 ~ '1280x720',
    trial_id %in% dg1920x1080 ~ '1920x1080',
    TRUE ~ 'None'
  )) %>%
  group_by(res) %>%
# Scale the 1980x1080 to same values as the 1280x720
  # mutate(
  #   x1=ifelse(trial_id %in% dg1920x1080, x1/1080*720, x1),
  #   y1=ifelse(trial_id %in% dg1920x1080, y1/1920*1280, y1),
  #   x2=ifelse(trial_id %in% dg1920x1080, x2/1080*720, x2),
  #   y2=ifelse(trial_id %in% dg1920x1080, y2/1920*1280, y2)
  # ) %>%
  # Z-score (mean center) the x1, y1, x2, y2 values? Then we do not have to normalize by wxh
  # Then we use that z-score to determine where the the point would be on a 1920x1080 image 
  mutate(
    z_x1=(x1-mean(x1, na.rm=T))/sd(x1, na.rm=T),
    z_y1=(y1-mean(y1, na.rm=T))/sd(y1, na.rm=T),
    z_x2=(x2-mean(x2, na.rm=T))/sd(x2, na.rm=T),
    z_y2=(y2-mean(y2, na.rm=T))/sd(y2, na.rm=T)
  ) %>%
  ungroup()

# Keep only the five most relevant tools
tools_of_interest <- c('suction', 'grasper', 'cottonoid', 'string', 'muscle')

# Will need to calculate proportions
total_frames_by_trial <- gt_fps1 %>%
  group_by(trial_id) %>%
  dplyr::summarise(total=length(unique(short_file_name)))

# Outcomes data
outcomes <- read_tsv('~/Documents/USC/USC_docs/ml/surgical-training-project/data/carotid_outcomes/complete_data_set.tsv')

training_successes <- outcomes %>% filter(`Trial 1 Success` == 0, `Trial 2 Success` == 1) %$% SurveyID
pros <- outcomes %>% filter(`Trial 1 Success` == 1, `Trial 2 Success` == 1) %$% SurveyID

outcomes_relevant <- outcomes %>% 
  dplyr::select(
    SurveyID,
    Group, endolast12mo, cadaverlast12,
    `Trial 1 TTH`, `Trial 2 TTH`, `Trial 1 Success`, `Trial 2 Success`) %>%
  gather(variable, value, -endolast12mo, -cadaverlast12, -Group, -SurveyID) %>%
  mutate(trial=stringr::str_extract(pattern='Trial [0-9]', string=variable)) %>%
  mutate(variable_name=gsub('.* ', '', variable)) %>%
  mutate(trial_id=paste0('S', SurveyID, 'T', stringr::str_extract(pattern='[0-9]', string=trial))) %>%
  dcast(trial_id + Group + endolast12mo + cadaverlast12 ~ variable_name, value.var='value')

unpaired_t1s <- c('S320T1', 'S310T1', 'S506T1', 'S314T1')
trials_to_ignore <- c('S314T2') # Ignoring this one because it is annotated far beyond TTH
```

```{r eval=FALSE}
ggplot(gt_fps1 %>% 
    filter(tool=='suction') %>%
    mutate(dim=case_when(trial_id %in% dg1280x720 ~ '1280x720', 
      trial_id %in% dg1920x1080 ~ '1980x1080',
      TRUE ~ 'None')), aes(x2)) +
  geom_density() +
  facet_wrap(~dim, scales = 'free')
```

```{r}
apms_dataframe <- total_frames_by_trial %>%
  filter(!(trial_id %in% trials_to_ignore)) %>%
  left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h), by = 'trial_id') %>%
  left_join(.,outcomes_relevant, by = 'trial_id')

apms_dataframe %<>% filter(!is.na(Success))
```

Below is a plot of the TTH from the outcomes data and the total frames annotated. There are some inconsistencies that we will want to make sure to address. In this analysis I am currently ignoring the following trials: `r paste0(trials_to_ignore, collapse=', ')`

```{r}
totals_v_tth <- total_frames_by_trial %>%
  left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h), by = 'trial_id') %>%
  left_join(.,outcomes_relevant, by = 'trial_id')

ggplot(totals_v_tth, aes(TTH, total)) +
  geom_point() +
  geom_text_repel(data=totals_v_tth %>% filter(abs(TTH-total) > 50), aes(label=trial_id))
```

The APMs used in this analysis are:

* Proportion of frames each tool is used in a trial (# of frames with tool/# frames in trial). Set to 0 if a tool is not used.

```{r}
# Frames each tool used
apms_dataframe %<>% left_join(
  ., 
  gt_fps1 %>%
    filter(tool %in% tools_of_interest) %>%
    group_by(trial_id, tool) %>%
    dplyr::summarise(count=length(unique(short_file_name))) %>%
    ungroup() %>%
    dplyr::mutate(tool=paste0('frames_with_', tool)) %>%
    dcast(trial_id ~ tool, value.var='count'),
  by = 'trial_id'
)
```

* Proportion of frames with 0, 1, 2, ... tools in view (# of frames with n tools/# frames in trial).
```{r}
# Frames 0, 1, 2, 3, 4+ tools in view
n_tools_in_view_ds <- gt_fps1 %>%
  filter(tool %in% tools_of_interest) %>%
  group_by(trial_id, short_file_name) %>%
  dplyr::summarise(n_tools=length(unique(tool))) %>%
  ungroup() %>%
  group_by(trial_id, n_tools) %>%
  dplyr::summarise(count=n()) %>%
  dplyr::mutate(n_tools=paste0('frames_with_', n_tools, '_tool(s)_in_view')) %>%
  dcast(trial_id ~ n_tools, value.var='count')

# Add the column for frames with at least one tool in view
n_tools_in_view_ds[,'frames_with_at_least_1_tool_in_view'] <- apply(n_tools_in_view_ds[,colnames(n_tools_in_view_ds)[grep('frames_with_[0-9]+_.*', colnames(n_tools_in_view_ds))]], 1, FUN = function(x) sum(x[!is.na(x)]))


apms_dataframe %<>% left_join(.,
  n_tools_in_view_ds,
  by = 'trial_id') %>%
  mutate(frames_with_0_tools_in_view=total-frames_with_at_least_1_tool_in_view)
```

* First frame that each tool appears in during the trial. If a tool does not appear in the trial, this feature is set to the length of the trial.
```{r}
# First frame that each tool appears
apms_dataframe %<>% left_join(.,
  gt_fps1 %>%
    filter(tool %in% tools_of_interest) %>%
    group_by(trial_id, tool) %>%
    dplyr::summarise(first_appear=min(frame)) %>%
    ungroup() %>%
    mutate(tool=paste0('first_frame_appear_', tool)) %>%
    dcast(trial_id ~ tool, value.var='first_appear'),
  by = 'trial_id')
```

* Number of in 'n' outs (renamed "tool exchanges"). This APM is calculated for each tool where we count the number of times a tool comes in and then out of screen. This is normalized by the total number of frames in the trial, so the feature can be interpretted as the number of in n outs / frame. Set to 0 if a tool is not used
```{r}
# Number of in n outs
# From https://stackoverflow.com/questions/16324897/finding-groups-of-contiguous-numbers-in-a-list
calc_in_n_outs <- function(x) {
  if (length(x) <= 1) {
    return(length(x))
  }
  
  x <- x[order(x)]
  
  ins <- c(1, which(diff(x) != 1 & diff(x) != 0) + 1)
  outs <- c(ins - 1, length(x)) 
  ranges <- (paste0(x[ins], '-', x[outs]))
  
  return(ranges)
}

apms_dataframe %<>% left_join(.,
  gt_fps1 %>%
    filter(tool %in% tools_of_interest) %>%
    group_by(trial_id, tool) %>%
    dplyr::summarise(in_n_outs=length(calc_in_n_outs(frame))) %>%
    ungroup() %>%
    mutate(tool=paste0('n_in_n_outs_', tool)) %>%
    dcast(trial_id ~ tool, value.var='in_n_outs'),
  by = 'trial_id')

apms_dataframe[,'total_in_n_outs'] <- apms_dataframe %>% 
  .[,grep('n_in_n_outs_', colnames(.))] %>%
  apply(., 1, FUN = function(x) sum(x, na.rm = T))
```

```{r eval=FALSE}
# In n outs in the first 30 seconds
first_30_seconds_exchanges <- gt_fps1 %>%
  filter(tool %in% tools_of_interest) %>%
  filter(frame < 60) %>%
  group_by(trial_id, tool) %>%
  dplyr::summarise(in_n_outs=length(calc_in_n_outs(frame))) %>%
  ungroup() %>%
  mutate(tool=paste0('n_in_n_outs_', tool)) %>%
  dcast(trial_id ~ tool, value.var='in_n_outs')

first_30_seconds_exchanges[,'first_30s_total_in_n_outs'] <- first_30_seconds_exchanges %>% 
  .[,grep('n_in_n_outs_', colnames(.))] %>%
  apply(., 1, FUN = function(x) sum(x, na.rm = T))

apms_dataframe %<>% left_join(., 
  first_30_seconds_exchanges[,c('trial_id', 'first_30s_total_in_n_outs')],
  by = 'trial_id'
)
```

```{r include=FALSE, eval=FALSE}
# * Time to 10 tool exchanges. How many seconds it took before a surgeon had 10 tool exchanges in a trial

time_to_n_exchanges <- function(data, n) {
  # Get ranges of each tool
  ranges_all <- c()
  for (to in unique(data$tool)) {
    ranges <- data %>%
      filter(tool==to) %$%
      calc_in_n_outs(frame)
    
    ranges_all <- c(ranges_all, ranges)
  }
  
  ranges_all <- ranges_all[order(as.numeric(gsub('\\-.*', '', ranges_all)))]

  res <- NA
  if (length(ranges_all) >= n) {
    r <- ranges_all[n]
    res <- as.numeric(stringr::str_extract(pattern = '^[0-9]+', string=r))
  }
  
  out <- data.frame(trial_id=unique(data$trial_id), res=res)
  out %<>% magrittr::set_colnames(c('trial_id', paste0('time_to_', n, '_exchanges')))
  return(out)
}

n_value <- 5

apms_dataframe %<>% left_join(.,
  gt_fps1 %>%
    filter(tool %in% tools_of_interest) %>%
    filter(tool == 'suction') %>%
    group_by(trial_id) %>%
    dplyr::do(time_to_n_exchanges(data=., n=n_value)),
  by = 'trial_id')
```

```{r eval=FALSE}
suction_only_fps1 <- gt_fps1 %>% 
  filter(tool=='suction') %>% 
  group_by(trial_id, tool) %>%
  dplyr::summarise(in_n_outs=length(calc_in_n_outs(frame, tool=unique(tool)))) %>%
  filter(trial_id %in% c('S306T1', 'S306T2', 'S611T1', 'S609T2'))

suction_only_fps10 <- read_csv('~/Documents/USC/USC_docs/ml/datasets/fps-10-uncropped/ImageSets/Main/retinanet_surgical_10fps_complete.csv',
    col_names = c('file', 'x1', 'y1', 'x2', 'y2', 'tool')) %>%
  mutate(short_file_name=gsub('.*/', '', file)) %>%
  mutate(trial_id=gsub('[a-z]?_.*', '', short_file_name)) %>%
  mutate(frame=as.numeric(stringr::str_extract(pattern='[0-9]+', string=gsub('.*_', '', short_file_name)))) %>% 
  filter(tool=='suction') %>% 
  group_by(trial_id, tool) %>%
  dplyr::summarise(in_n_outs=length(calc_in_n_outs(frame, tool=unique(tool)))) %>%
  filter(trial_id %in% c('S306T1', 'S306T2', 'S611T1', 'S609T2'))

suction_only_fps30 <- read_csv('~/Documents/USC/USC_docs/ml/datasets/fps-30-uncropped/ImageSets/Main/local_retinanet_style.csv',
    col_names = c('file', 'x1', 'y1', 'x2', 'y2', 'tool')) %>%
  mutate(short_file_name=gsub('.*/', '', file)) %>%
  mutate(trial_id=gsub('[a-z]?_.*', '', short_file_name)) %>%
  mutate(frame=as.numeric(stringr::str_extract(pattern='[0-9]+', string=gsub('.*_', '', short_file_name)))) %>% 
  filter(tool=='suction') %>% 
  group_by(trial_id, tool) %>%
  dplyr::summarise(in_n_outs=length(calc_in_n_outs(frame, tool=unique(tool)))) %>%
  filter(trial_id %in% c('S306T1', 'S306T2', 'S611T1', 'S609T2'))

combined_inouts_fps <- suction_only_fps1 %>%
  dplyr::select(trial_id, fps1=in_n_outs) %>%
  left_join(., suction_only_fps10 %>% dplyr::select(trial_id, fps10=in_n_outs), by='trial_id') %>%
  left_join(., suction_only_fps30 %>% dplyr::select(trial_id, fps30=in_n_outs), by='trial_id')

combined_inouts_fps
```

* Area covered by each tool. This APM is calculated by summing the area of the bounding boxes for a tool in each frame and dividing it by the total number of frames in the trial.  
```{r}
area_data <- gt_fps1 %>%
  # mutate(area = (y2-y1)*(x2-x1)) %>%
  mutate(area = ifelse(is.na(y2) | is.na(x2-x1), 0, (y2-y1)*(x2-x1))) %>%
  filter(tool %in% tools_of_interest) %>%
  # to z-score
  # group_by(tool, res) %>%
  # mutate(area=(area- mean(area, na.rm=T))/sd(area, na.rm=T)) %>%
  # ungroup() %>%
  group_by(trial_id, tool) %>%
  dplyr::summarise(area_covered=sum(area)) %>%
  ungroup() %>%
  mutate(tool=paste0('area_covered_', tool)) %>%
  dcast(trial_id ~ tool, value.var='area_covered')

# Total area covered by boxes (needs to be normalized to the size of the frame)
apms_dataframe %<>% left_join(., 
  area_data,
  by = 'trial_id')

# Normalize area by the size of the frame and the total number of frames
apms_dataframe[,colnames(apms_dataframe)[grep('area_covered_', colnames(apms_dataframe))]] <- apms_dataframe[,colnames(apms_dataframe)[grep('area_covered_', colnames(apms_dataframe))]]/(apms_dataframe$w * apms_dataframe$h)/apms_dataframe$total
```

```{r}
# For PCA
pca_area <- apms_dataframe %>%
  dplyr::select(c('trial_id', colnames(.)[grep('area', colnames(.))])) %>%
  # filter(trial_id %in% (apms_dataframe %>% filter(Success == 1) %$% trial_id)) %>%
  .[complete.cases(.),] %>%
  as.data.frame()

row.names(pca_area) <- pca_area$trial_id
pca_area$trial_id <- NULL

pca_area_res <- prcomp(pca_area)
pca_area_plot <- pca_area_res$x %>%
  as.data.frame() %>%
  mutate(trial_id=row.names(.)) %>%
  left_join(., apms_dataframe %>% dplyr::select(trial_id, total, Success), by='trial_id') %>%
  left_join(., frame_dimensions, by='trial_id') %>%
  mutate(res=paste0(w, 'x', h)) %>%
  filter(!is.na(Success)) %>%
  mutate(Success=paste0('Success: ', Success))

# pca_plot %$%
  # t.test(PC1[which(res == '1920x1080')], PC1[which(res != '1920x1080')])

ggplot(pca_area_plot, aes(PC1, PC2, color=res)) +
  geom_point() +
  facet_wrap(~Success) +
  theme(legend.position = 'top')
```

* Standard of deviation of each of the coordinates for each tool. Also of the center x and center y.
```{r include=FALSE}
sd_data <- gt_fps1 %>%
  dplyr::select(-res) %>%
  filter(tool %in% tools_of_interest) %>%
  left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h), by='trial_id') %>%
  mutate(x1=x1/w, y1=y1/h, x2=x2/w, y2=y2/h) %>% # Normalized by w x h
  # mutate(cx=(x1+x2)/2, cy=(y1+y2)/2) %>%
  # mutate(center_single_point=sqrt(cx^2+cy^2)) %>%
  gather(variable, value, -file, -tool, -short_file_name, -trial_id, -frame, -w, -h) %>%
  group_by(trial_id, tool, variable) %>%
  dplyr::summarise(
    sd=sd(value)
  ) %>%
  ungroup() %>%
  mutate(tool=paste0('sd_', variable, '_', tool)) %>%
  dcast(trial_id ~ tool, value.var='sd')

apms_dataframe %<>% left_join(., 
  sd_data,
  by = 'trial_id')
```

PCA plot to see if there are any batch effects when in the standard deviations based on resolution

```{r}
# For PCA
pca_sd <- sd_data %>%
  dplyr::select(c('trial_id', colnames(.)[grep('sd_[xy]', colnames(.))])) %>%
  # filter(trial_id %in% (apms_dataframe %>% filter(Success == 1) %$% trial_id)) %>%
  .[complete.cases(.),]

row.names(pca_sd) <- pca_sd$trial_id
pca_sd$trial_id <- NULL

pca_res <- prcomp(pca_sd)
pca_plot <- pca_res$x %>%
  as.data.frame() %>%
  mutate(trial_id=row.names(.)) %>%
  left_join(., apms_dataframe %>% dplyr::select(trial_id, total, Success), by='trial_id') %>%
  left_join(., frame_dimensions, by='trial_id') %>%
  mutate(res=paste0(w, 'x', h)) %>%
  filter(!is.na(Success)) %>%
  mutate(Success=paste0('Success: ', Success))

# pca_plot %$%
  # t.test(PC1[which(res == '1920x1080')], PC1[which(res != '1920x1080')])

ggplot(pca_plot, aes(PC1, PC2, color=res)) +
  geom_point() +
  facet_wrap(~Success) +
  theme(legend.position = 'top')
```

* Distance traveled by each tool. Calculated from the top of the tool box if tool is suction or grasper and center of the box for muscle and cottonoid
* Tool speed - takes the distance traveled and divides by the total number of frames the tool is present

```{r}
# Distance traveled by each tool
get_dist_tool <- function(tid, to, normalize=F) {
  # Get all frames with that tool
  # tid = 'S301T1'
  # to = 'suction'
  relevant_frames <- gt_fps1 %>% filter(trial_id == tid, tool == to)
  total_frames <- total_frames_by_trial %>% filter(trial_id == tid) %$% total[1]
  
  frame_coordinates_all <- data.frame(frame=seq(1, total_frames)) %>%
    left_join(., relevant_frames %>% 
        dplyr::select(frame, tool, x1, x2, y1, y2) %>%
        mutate(x=(x1+x2)/2, y = ifelse(tool %in% c('suction', 'grasper'), y1, (y1+y2)/2)) %>%
        dplyr::select(frame, tool, x, y), by = 'frame')
  
  # Have to normalize
  w <- frame_dimensions %>% filter(trial_id == tid) %$% w
  h <- frame_dimensions %>% filter(trial_id == tid) %$% h
  
  x1 <- frame_coordinates_all$x %>% .[1:length(.)-1]/w
  x2 <- frame_coordinates_all$x %>% .[2:length(.)]/w
  
  y1 <- frame_coordinates_all$y %>% .[1:length(.)-1] /h
  y2 <- frame_coordinates_all$y %>% .[2:length(.)] /h
  
  distance_covered <- sqrt((x2-x1)^2 + (y2-y1)^2)
  
  # Normalize by total frames present (giving us speed)
  if (normalize) {
    distance_covered <- distance_covered/length(which(!is.na(distance_covered)))
  }
  
  return(sum(distance_covered, na.rm=T))
}

distance_covered_apm <- gt_fps1 %>%
  left_join(., frame_dimensions, by='trial_id') %>%
  filter(tool %in% tools_of_interest) %>% 
  distinct(trial_id, tool) %>%
  group_by(trial_id, tool) %>%
  mutate(distance_covered=get_dist_tool(tid=trial_id, to=tool)) %>%
  ungroup() %>%
  mutate(tool=paste0('distance_covered_', tool)) %>%
  dcast(trial_id ~ tool, value.var='distance_covered')

distance_covered_normalized_apm <- gt_fps1 %>%
  # dplyr::select(-x1, -y1, -x2, -y2) %>%
  # dplyr::rename(x1=z_x1, x2=z_x2, y1=z_y1, y2=z_y2) %>%
  filter(tool %in% tools_of_interest) %>% 
  distinct(trial_id, tool) %>%
  group_by(trial_id, tool) %>%
  mutate(distance_covered=get_dist_tool(tid=trial_id, to=tool, normalize = T)) %>%
  ungroup() %>%
  mutate(tool=paste0('tool_speed_', tool)) %>%
  dcast(trial_id ~ tool, value.var='distance_covered')

apms_dataframe %<>% left_join(., distance_covered_apm, by = 'trial_id')
apms_dataframe %<>% left_join(., distance_covered_normalized_apm, by = 'trial_id')
```

Looking for potential batch effects in how distance traveled is calculated (by resolution). Done using PCA and looking at PC1 and PC2

```{r}
# Looking at potential batch effects in Area
pca_dist <- distance_covered_apm %>%
  dplyr::select(c('trial_id', colnames(.)[grep('distance', colnames(.))])) %>%
  # filter(trial_id %in% (apms_dataframe %>% filter(Success == 1) %$% trial_id)) %>%
  .[complete.cases(.),]

row.names(pca_dist) <- pca_dist$trial_id
pca_dist$trial_id <- NULL

pca_dist_res <- prcomp(pca_dist)
pca_dist_plot <- pca_dist_res$x %>%
  as.data.frame() %>%
  mutate(trial_id=row.names(.)) %>%
  left_join(., apms_dataframe %>% dplyr::select(trial_id, total, Success), by='trial_id') %>%
  left_join(., frame_dimensions, by='trial_id') %>%
  mutate(res=paste0(w, 'x', h)) %>%
  filter(!is.na(Success)) %>%
  mutate(Success=paste0('Success: ', Success))

ggplot(pca_dist_plot, aes(PC1, PC2, color=res)) +
  geom_point() +
  facet_wrap(~Success) +
  theme(legend.position = 'top')
```

* Overlap of tools. Number of frames where two tools overlap by greater than > x using IoU. Doing this for suction + cottonoid and grasper + muscle

```{r}
# Need function that looks for the overlap of two boxes (Aoverlap/ A1 +A2 - Aoverlap)
intersection_over_union <- function(b1, b2) {
  if (is.na(b1[1]) | is.na(b2[1])) {
    return(0)
  }
  
  b1 <- as.numeric(b1)
  b2 <- as.numeric(b2)
  
  x1 <- max(b1[1], b2[1])
  y1 <- max(b1[2], b2[2])
  x2 <- min(b1[3], b2[3])
  y2 <- min(b1[4], b2[4])
  
  if ((x2 < x1) | (y2 < y1)) {
    return(0)
  }
  
  a1 <- (b1[3] - b1[1]) * (b1[4] - b1[2])
  a2 <- (b2[3] - b2[1]) * (b2[4] - b2[2])
  
  # A overlap
  ao = (x2 - x1) * (y2 - y1)
  
  return(ao/(a1 + a2 - ao))
}

# Suction + cottonoid
frames_with_tools <- list()
for (to in c('suction', 'grasper', 'cottonoid', 'muscle')) {
  frames_with_tools[[to]] <- suction_frames <- gt_fps1 %>%
    filter(tool==to) %>%
    left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h), by='trial_id') %>%
    # mutate(x1=x1/w, y1=y1/h, x2=x2/w, y2=y2/h) %>%
    dplyr::select(trial_id, frame, x1, y1, x2, y2)
}

# Sincle data frame
combined_suction_cottonoids <- merge(
  frames_with_tools$suction %>% 
    dplyr::rename(t1_x1=x1, t1_y1=y1, t1_x2=x2, t1_y2=y2), 
  frames_with_tools$cottonoid %>% 
    dplyr::rename(t2_x1=x1, t2_y1=y1, t2_x2=x2, t2_y2=y2), 
  by=c('trial_id', 'frame')
) %>% filter(!is.na(t1_x1) & !is.na(t2_x1))

combined_grasper_muscle <- merge(
  frames_with_tools$grasper %>% 
    dplyr::rename(t1_x1=x1, t1_y1=y1, t1_x2=x2, t1_y2=y2), 
  frames_with_tools$muscle %>% 
    dplyr::rename(t2_x1=x1, t2_y1=y1, t2_x2=x2, t2_y2=y2), 
  by=c('trial_id', 'frame')
) %>% filter(!is.na(t1_x1) & !is.na(t2_x1))

sc_areas <- apply(combined_suction_cottonoids, 1, FUN = function(x) {
  intersection_over_union(
    c(x[['t1_x1']], x[['t1_y1']], x[['t1_x2']], x[['t1_y2']]),
    c(x[['t2_x1']], x[['t2_y1']], x[['t2_x2']], x[['t2_y2']])
  )
})

gm_areas <- apply(combined_grasper_muscle, 1, FUN = function(x) {
  intersection_over_union(
    c(x[['t1_x1']], x[['t1_y1']], x[['t1_x2']], x[['t1_y2']]),
    c(x[['t2_x1']], x[['t2_y1']], x[['t2_x2']], x[['t2_y2']])
  )
})

combined_suction_cottonoids[,'overlap'] <- sc_areas
combined_grasper_muscle[,'overlap'] <- gm_areas

# Overlap threshold
sc_overlap <- 0.15
gm_overlap <- 0.05

apms_dataframe %<>% left_join(.,  
  combined_suction_cottonoids %>%
    filter(overlap > sc_overlap) %>%
    group_by(trial_id) %>%
    dplyr::summarise(overlap_sc=n()),
  by='trial_id') %>% 
  mutate(overlap_sc=overlap_sc/total) %>%
  mutate(got_to_sc_step=ifelse(overlap_sc > 0, 1, 0))

apms_dataframe %<>% left_join(.,  
  combined_grasper_muscle %>%
    filter(overlap > gm_overlap) %>%
    group_by(trial_id) %>%
    dplyr::summarise(overlap_gm=n()),
  by='trial_id') %>% 
  mutate(overlap_gm=overlap_gm/total) %>%
  mutate(got_to_gm_step=ifelse(overlap_gm > 0, 1, 0))
# 
# # Success examples
# success <- apms_dataframe %>% filter(Success==1) %$% trial_id[1:10]
# 
# ggplot(combined_grasper_muscle %>% filter(trial_id %in% success[3]), aes(frame, overlap)) +
#   geom_point()
```

```{r eval=FALSE}
# * % dwell time in each quadrant. For each tool, what % of time of the trial is spent in each quadrant
gt_fps1 %>%
  filter(tool %in% tools_of_interest) %>%
  left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h)) %>%
  # mutate(x1=x1/w, y1=y1/h, x2=x2/w, y2=y2/h) %>%
  mutate(cx=(x1+x2)/2, cy=(y1+y2)/2) %>%
  mutate(quadrant=case_when(
    (cx < 0.5 & cy < 0.5) ~ 'TL',
    (cx < 0.5 & cy >= 0.5) ~ 'BL',
    (cx > 0.5 & cy < 0.5) ~ 'TR',
    (cx > 0.5 & cy >= 0.5) ~ 'BR',
    TRUE ~ 'None'
  )) %>%
  group_by(trial_id, tool, quadrant) %>%
  dplyr::summarise(
    count=n()
  ) %>%
  ungroup() %>%
  mutate(tool=paste0('quadrant_', quadrant, '_', tool)) %>%
  dcast(trial_id ~ tool, value.var='count')
```

```{r}
# Replace NAs with 0s
apms_dataframe %<>% filter(trial_id != 'S608T3')

# Not for except for first frame, where if it is NA we will replace with the length of the trial
apms_dataframe[,c('total', colnames(apms_dataframe)[grep('^first_frame_', colnames(apms_dataframe))])] %<>%
  apply(., 1, FUN = function(x) { ifelse(is.na(x), x[['total']], x)}) %>% t()


# summary(apms_dataframe)
# apms_dataframe[is.na(apms_dataframe)] <- 0
apms_dataframe[, grep('^(frames|overlap|got_to|distance|n_in_n_outs)_', colnames(apms_dataframe))] %<>% 
  apply(., 1, FUN = function(x) ifelse(is.na(x), 0, x)) %>%
  t()

# Normalize by total number of frames
apms_dataframe[,grep('^frames_', colnames(apms_dataframe))] <- apms_dataframe[,grep('^frames_', colnames(apms_dataframe))]/apms_dataframe$total
# Quadrant dwell time - need to figure out how to normalize (or else just becomes a proxy for tool use)
# apms_dataframe[,grep('^quadrant_', colnames(apms_dataframe))] <- apms_dataframe[,grep('^quadrant_', colnames(apms_dataframe))]/apms_dataframe$total
# apms_dataframe[,grep('^n_in_n_outs', colnames(apms_dataframe))] <- apms_dataframe[,grep('^n_in_n_outs', colnames(apms_dataframe))]/apms_dataframe$total
```

## Looking at potential batch effects

In the positional based APMs, there could be batch effects from the different resolutions used. If a disproportionate amount of successes were filmed in 1920 x 1080 vs. 1280 x 720, these tests could be picking up on that rather than actually picking up on differences in performance.

To assess, we will perfrom t-tests comparing the two cohorts

### Successes only

Looking only at successful trials, do we see differences in the metrics when we split based on resolution

```{r eval=FALSE}
length(intersect(dg1280x720, c(paste0('S', training_successes, 'T1'), paste0('S', training_successes, 'T2'))))

length(intersect(dg1920x1080, c(paste0('S', training_successes, 'T1'), paste0('S', training_successes, 'T2'))))
```

```{r}
# summary(apms_dataframe)

batch_successes_apms_test_p_vals <- apms_dataframe %>%
  filter(Success==1) %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH) %>%
  # filter(grepl('', variable)) %>%
  group_by(variable) %>%
  dplyr::summarise(
    m_dg1920x1080=mean(value[which(trial_id %in% dg1920x1080)], na.rm=T),
    n_dg1920x1080=length(intersect(which(trial_id %in% dg1920x1080), which(!is.na(value)))),
    m_dg1280x720=mean(value[which(trial_id %in% dg1280x720)], na.rm=T),
    sd=sd(value, na.rm=T),
    n_dg1280x720=length(intersect(which(trial_id %in% dg1280x720), which(!is.na(value)))),
    p.value=t.test(value[which(trial_id %in% dg1920x1080)], value[which(trial_id %in% dg1280x720)])$p.value
  )

batch_success_dims <- batch_successes_apms_test_p_vals %>%
  mutate(effect_size=m_dg1280x720-m_dg1920x1080) %>%
  mutate(`es/sd`=(m_dg1280x720-m_dg1920x1080)/sd) %>%
  dplyr::arrange(p.value)  %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

batch_success_dims[,grep('^(m|sd|effect|es)', colnames(batch_success_dims))] %<>% apply(., 2, FUN = function(x) round(x, 3))

batch_success_dims %>%
  DT::datatable(options = list(scrollX=TRUE))
```

```{r eval=FALSE}
# Plot the sd of everything 
summary(apms_dataframe)

pixel_based_metrics <- colnames(apms_dataframe) %>%
  .[grep('^(area|sd|distance|tool_speed|overlap)', .)]

pixel_based_plot_data <- apms_dataframe %>%
  filter(Success==0) %>%
  dplyr::select(c('trial_id', 'w', 'h', pixel_based_metrics)) %>%
  gather(variable, value, -trial_id, -w, -h) %>%
  mutate(g=paste0(w, 'x', h))

ggplot(pixel_based_plot_data %>% filter(grepl('distance', variable)), aes(variable, value, fill=g)) +
  geom_boxplot(outlier.colour = NA) +
  geom_point(aes(color=g), position = position_jitterdodge(), size=0.25) +
  theme(
    legend.position = 'top',
    legend.justification = 'left',
    axis.text.x = element_text(angle=90, hjust=1, vjust = 0.5)
  )
```

### Failures only

Same thing as above but for failures only

```{r}
batch_failures_apms_test_p_vals <- apms_dataframe %>%
  filter(Success==0) %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH) %>%
  group_by(variable) %>%
  dplyr::summarise(
    m_dg1920x1080=mean(value[which(trial_id %in% dg1920x1080)], na.rm = T),
    n_dg1920x1080=length(intersect(which(trial_id %in% dg1920x1080), which(!is.na(value)))),
    m_dg1280x720=mean(value[which(trial_id %in% dg1280x720)], na.rm = T),
    n_dg1280x720=length(intersect(which(trial_id %in% dg1280x720), which(!is.na(value)))),
    sd=sd(value, na.rm = T),
    p.value=t.test(value[which(trial_id %in% dg1920x1080)], value[which(trial_id %in% dg1280x720)])$p.value
  )

batch_failures_dims <- batch_failures_apms_test_p_vals %>%
  mutate(effect_size=m_dg1280x720-m_dg1920x1080) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

batch_failures_dims[,grep('^(m|sd|effect|es)', colnames(batch_failures_dims))] %<>% apply(., 2, FUN = function(x) round(x, 3))

batch_failures_dims %>%
  DT::datatable(options = list(scrollX=TRUE))
```

```{r eval=FALSE}
head(apms_dataframe)

ggplot(apms_dataframe %>% 
    mutate(res=case_when(
      trial_id %in% dg1280x720 ~ '1280x720', 
      trial_id %in% dg1920x1080 ~ '1920x1080', 
      TRUE ~ 'None')) %>%
    filter(trial_id %in% c(paste0('S', training_successes, 'T1'), paste0('S', training_successes, 'T2'))) %>%
    mutate(Success=factor(Success)), aes(sd_cx_suction, sd_cy_suction, color=Success)) +
  geom_point() +
  facet_wrap(~res)
```

## Successes vs. Failures

### t-tests no correction

t-tests comparing all successful trials vs. failures. Not correcting for any batch effects due to resolution

```{r}
apms_test_p_vals <- apms_dataframe %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH) %>%
  group_by(variable) %>%
  dplyr::summarise(
    m_fail=mean(value[which(Success==0)], na.rm = T),
    n_fail=length(intersect(which(Success==0), which(!is.na(value)))),
    m_success=mean(value[which(Success==1)], na.rm = T),
    n_success=length(intersect(which(Success==1), which(!is.na(value)))),
    sd=sd(value,na.rm=T),
    p.value=t.test(value[which(Success==0)], value[which(Success==1)])$p.value
  )

s_v_f <- apms_test_p_vals %>%
  mutate(effect_size=m_success-m_fail) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

s_v_f[,grep('^(m|sd|effect|es)', colnames(s_v_f))] %<>% apply(., 2, FUN = function(x) round(x, 3))

s_v_f %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/apms_success_v_failure.tsv', row.names=F, quote=F, sep = '\t')

s_v_f %>%
  DT::datatable(options = list(scrollX=TRUE))
```

### Correcting for batch effects

For this, we fit a linear model that includes a parameter for resolution and a parameter for the independent variable. The effect size reported is the coefficient of the variable and the p-value is its significance

```{r include=FALSE}
fit_model_with_correction <- function(data, dep_var='Success') {
  # Write the formula
  model_formula <- as.formula(paste0('value~res+', dep_var))
  
  # print(model_formula)
  
  model_res <- lm(model_formula, data=data %>% mutate(res=factor(res))) %>% 
    summary() %>% 
    coefficients()

  # print(which(data[,dep_var]==0))
  
  mean0 <- mean(data$value[which(data[,dep_var]==0)])
  mean1 <- mean(data$value[which(data[,dep_var]==1)])
  
  # print(mean0)
    
  out <- data.frame(
    variable=unique(data$variable), 
    resolution_estimate=model_res[2,1], resolution_p=model_res[2,4],
    dep_estimate=model_res[3,1], dep_p=model_res[3,4],
    n_dep=length(which(data[,dep_var]==1)), 
    m0=mean0, m1=mean1
  ) %>% magrittr::set_colnames(
    c(
      'variable', 
      'resolution_estimate', 
      'resolution_p', 
      'dep_estimate', 
      'dep_p', 
      paste0(dep_var, '=1 (n)'), 
      paste0('mean ', dep_var, '=0'), 
      paste0('mean ', dep_var, '=1')))
  
  return(out)
}


apms_lm_p_vals <- apms_dataframe %>%
  mutate(res=case_when(
      trial_id %in% dg1280x720 ~ '1280x720', 
      trial_id %in% dg1920x1080 ~ '1920x1080', 
      TRUE ~ 'None')) %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH, -res) %>%
  # filter(variable=='Group') %>%
  group_by(variable) %>%
  dplyr::do(fit_model_with_correction(data=., dep_var='Success'))
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
apms_lm_p_vals[,grep('estimate|mean', colnames(apms_lm_p_vals))] %<>% apply(., 2, FUN = function(x) round(x, 3))

apms_lm_p_vals %>%
  arrange(dep_p) %>%
  dplyr::mutate(dep_p=format(dep_p, digits=3)) %>%
  dplyr::mutate(resolution_p=format(resolution_p, digits=3)) %>%
  datatable(options=list(scrollX=T))
```

## Training Successes T1 vs. T2

t-tests comparing T1 vs. T2 in training successes. No batch effect correction used

```{r}
# Get the training successes and compare their trial 1s vs. their trial 2s
training_successes_t1_vs_t2 <- apms_dataframe %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  filter(trial_id %in% c(paste0('S', training_successes, 'T1'), paste0('S', training_successes, 'T2'))) %>%
  # filter out trial that is unpaired
  filter(!(trial_id %in% unpaired_t1s)) %>% # These don't have a matched T2
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH) %>%
  group_by(variable) %>%
  dplyr::summarise(
    t1=mean(value[which(Success==0)], na.rm = T),
    n_t1=length(intersect(which(Success==0), which(!is.na(value)))),
    t2=mean(value[which(Success==1)], na.rm = T),
    n_t2=length(intersect(which(Success==1), which(!is.na(value)))),
    sd=sd(value, na.rm=T),
    p.value=t.test(
      (value[which(Success==0)] %>% .[order(trial_id)]), 
      (value[which(Success==1)] %>% .[order(trial_id)]), 
      paired = TRUE
      )$p.value
  )

ts_t1_v_t2 <- training_successes_t1_vs_t2 %>%
  mutate(effect_size=t2-t1) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

ts_t1_v_t2[,grep('^(t1|t2|m|sd|effect|es)', colnames(ts_t1_v_t2))] %<>% apply(., 2, FUN = function(x) round(x, 3))

ts_t1_v_t2 %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/successes_t1_v_t2.tsv', quote=F, row.names=F, sep = '\t')

ts_t1_v_t2 %>%
  DT::datatable(options=list(scrollX=TRUE))
```

## Training Success vs. Pros

t-test Training Successes T2 vs. Pros T2. No batch correction used

```{r}
# Compare the training success trial 2 to pros (combined trial 1 and 2)
pros_v_training_success_t2 <- apms_dataframe %>%
  mutate(Group=ifelse(Group=='Attending', 1, 0)) %>%
  filter(trial_id %in% c(paste0('S', training_successes, 'T2'), paste0('S', pros, 'T2'))) %>%
  mutate(Split=ifelse(trial_id %in% paste0('S', training_successes, 'T2'), 'Success', 'Pro')) %>%
  # filter out trial that is unpaired
  filter(!(trial_id %in% unpaired_t1s)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH, -Split) %>%
  group_by(variable) %>%
  dplyr::summarise(
    TS=mean(value[which(Split=='Success')], na.rm = T),
    Pro=mean(value[which(Split=='Pro')], na.rm = T),
    n_TS=length(intersect(which(Split=='Success'), which(!is.na(value)))),
    n_Pro=length(intersect(which(Split=='Pro'), which(!is.na(value)))),
    sd=sd(value, na.rm=T),
    p.value=t.test(
      value[which(Split=='Success')], 
      value[which(Split=='Pro')]
      )$p.value
  )

p_vs_ts_t2 <- pros_v_training_success_t2 %>%
  mutate(effect_size=Pro-TS) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

p_vs_ts_t2[,grep('^(TS|Pro|m|sd|effect|es)', colnames(p_vs_ts_t2))] %<>% apply(., 2, FUN = function(x) round(x, 3))

p_vs_ts_t2 %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/t2s_successes_vs_pros.tsv', quote=F, row.names=F, sep = '\t')

p_vs_ts_t2 %>%
  DT::datatable(options=list(scrollX=TRUE))
```

## Attendings vs. Trainees

None of this analysis uses batch correction

### All trials

t-tests comparing attendings vs. trainees for all trials

```{r}
attending_vs_resident <- apms_dataframe %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH, -Group) %>%
  group_by(variable) %>%
  dplyr::summarise(
    Attending=mean(value[which(Group=='Attending')], na.rm = T),
    Trainee=mean(value[which(Group=='Trainee')], na.rm = T),
    n_A=length(intersect(which(Group=='Attending'), which(!is.na(value)))),
    n_T=length(intersect(which(Group=='Trainee'), which(!is.na(value)))),
    sd=sd(value, na.rm=T),
    p.value=t.test(
      value[which(Group=='Attending')], 
      value[which(Group=='Trainee')]
      )$p.value
  )

a_v_r_all_trials <- attending_vs_resident %>%
  mutate(effect_size=Attending-Trainee) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

a_v_r_all_trials[,grep('^(Attending|Trainee|m|sd|effect|es)', colnames(a_v_r_all_trials))] %<>% apply(., 2, FUN = function(x) round(x, 3))

a_v_r_all_trials %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/attending_v_trainee.tsv', quote=F, row.names=F, sep = '\t')

a_v_r_all_trials %>%
  DT::datatable(options=list(scrollX=TRUE))
```

### T1 only

```{r}
# Attending vs. resident trial 1 only
attending_vs_resident_t1_only <- apms_dataframe %>%
  filter(grepl('T1$', trial_id)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH, -Group) %>%
  group_by(variable) %>%
  dplyr::summarise(
    Attending=mean(value[which(Group=='Attending')], na.rm = T),
    Trainee=mean(value[which(Group=='Trainee')], na.rm = T),
    n_A=length(intersect(which(Group=='Attending'), which(!is.na(value)))),
    n_T=length(intersect(which(Group=='Trainee'), which(!is.na(value)))),
    sd=sd(value, na.rm=T),
    p.value=t.test(
      value[which(Group=='Attending')], 
      value[which(Group=='Trainee')]
      )$p.value
  )

a_v_r_t1 <- attending_vs_resident_t1_only %>%
  mutate(effect_size=Attending-Trainee) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

a_v_r_t1[,grep('^(Attending|Trainee|m|sd|effect|es)', colnames(a_v_r_t1))] %<>% apply(., 2, FUN = function(x) ifelse(is.na(x), NA, round(x, 3)))

a_v_r_t1 %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/attending_v_trainee_t1_only.tsv', quote=F, row.names=F, sep = '\t')

a_v_r_t1 %>%
  DT::datatable(options=list(scrollX=TRUE))
```

### Trial 2 only

```{r}
# Attending vs. resident trial 2 only
attending_vs_resident_t2_only <- apms_dataframe %>%
  filter(grepl('T2$', trial_id)) %>%
  gather(variable, value, -trial_id, -total, -w, -h, -Success, -TTH, -Group) %>%
  group_by(variable) %>%
  dplyr::summarise(
    Attending=mean(value[which(Group=='Attending')], na.rm = T),
    Trainee=mean(value[which(Group=='Trainee')], na.rm = T),
    n_A=length(intersect(which(Group=='Attending'), which(!is.na(value)))),
    n_T=length(intersect(which(Group=='Trainee'), which(!is.na(value)))),
    sd=sd(value, na.rm=T),
    p.value=t.test(
      value[which(Group=='Attending')], 
      value[which(Group=='Trainee')]
      )$p.value
  )

a_v_r_t2 <- attending_vs_resident_t2_only %>%
  mutate(effect_size=Attending-Trainee) %>%
  mutate(`es/sd`=effect_size/sd) %>%
  dplyr::arrange(p.value) %>%
  dplyr::mutate(p.value=format(p.value, digits=3))

a_v_r_t2[,grep('^(Attending|Trainee|m|sd|effect|es)', colnames(a_v_r_t2))] %<>% apply(., 2, FUN = function(x) round(x, 3))

a_v_r_t2 %>%
  write.table(., file = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/attending_v_trainee_t2_only.tsv', quote=F, row.names=F, sep = '\t')

a_v_r_t2 %>%
  DT::datatable(options=list(scrollX=TRUE))
```

## Success vs. Failure Visualizations

Simple scatter plot of the tool locations for successes and failures 

```{r eval=FALSE}
trials_ids_ordered_tth <- total_frames_by_trial %>%
  arrange(total) %$% 
  trial_id

# x-y plot success vs. failure
scatter_plot_test <- gt_fps1 %>% 
  # filter(trial_id %in% c('S303T1', 'S303T2')) %>%
  left_join(., frame_dimensions %>% dplyr::select(trial_id, w, h), by='trial_id') %>%
  left_join(., outcomes_relevant, by='trial_id') %>%
  mutate(Success=ifelse(Success==1, 'Success', 'Failure')) %>%
  mutate(trial_id=factor(trial_id, levels=trials_ids_ordered_tth))

# For suction and grasper -> we will do tool tip (mid point of top row)
# For cottonoid and muscle -> we will do the center
# We will ignore all other tools for now

parsed_data <- scatter_plot_test %>%
  filter(tool %in% c('suction', 'grasper', 'cottonoid', 'muscle')) %>%
  mutate(plot_y=case_when(
    tool %in% c('suction', 'grasper') ~ 1-y1/h,
    TRUE ~ 1-((y1+y2)/2)/h
  ), plot_x=(x1+x2)/2/w)

plot_scatter_tool_use <- function(data, fn) {
  g1 <- ggplot(data, aes(plot_x, plot_y, color=tool)) +
    geom_point() +
    scale_x_continuous(limits = c(0,1)) +
    scale_y_continuous(limits = c(0,1)) +
    facet_wrap(~trial_id) +
    theme_bw() +
    theme(
      legend.position = 'top',
      legend.justification = 'left'
    )
  
  ggsave(g1, filename = file.path(plot_dir, 'scatters-tools', fn), width = 8, height = 10)

}

# All tools
plot_scatter_tool_use(
  data = parsed_data %>% filter(Success=='Failure'),
  fn = 'failures_scatter.pdf')

plot_scatter_tool_use(
  data = parsed_data %>% filter(Success=='Success'),
  fn = 'successes_scatter.pdf')

# Each tool split
for (to in c('suction', 'grasper', 'cottonoid', 'muscle')) {
  plot_scatter_tool_use(
    data = parsed_data %>% filter(Success=='Failure', tool==to),
    fn = paste0(to, '_failure_scatter.pdf')
  )
  
  plot_scatter_tool_use(
    data = parsed_data %>% filter(Success=='Success', tool==to),
    fn = paste0(to, '_success_scatter.pdf')
  )
}
```

```{r eval=FALSE}
# Training successes, single plot side by side for easy interpretation
rescues_t1 <- training_successes %>% paste0('S', ., 'T1')
rescues_t2 <- training_successes %>% paste0('S', ., 'T2')

paired_order <- c(
  rescues_t1 %>% intersect(., parsed_data$trial_id) %>% setdiff(., unpaired_t1s),
  rescues_t2 %>% intersect(., parsed_data$trial_id)
) %>% .[order(.)]

resuces_plot_data <- parsed_data %>%
  filter(trial_id %in% paired_order) %>%
  mutate(trial_id=factor(trial_id, levels=paired_order))

rescues_all <- ggplot(resuces_plot_data, aes(plot_x, plot_y, color=tool)) +
    geom_point() +
    scale_x_continuous(limits = c(0,1)) +
    scale_y_continuous(limits = c(0,1)) +
    facet_wrap(~trial_id, ncol=2) +
    theme_bw() +
    theme(
      legend.position = 'top',
      legend.justification = 'left'
    )

ggsave(
  rescues_all,
  filename = file.path(plot_dir, 'scatters-tools', 'training_rescues_scatter.pdf'), 
  width = 4, height = 24)
  
for (to in c('suction', 'grasper', 'cottonoid', 'muscle')) {
  r_tool <- ggplot(resuces_plot_data %>% filter(tool==to), aes(plot_x, plot_y, color=tool)) +
    geom_point() +
    scale_x_continuous(limits = c(0,1)) +
    scale_y_continuous(limits = c(0,1)) +
    facet_wrap(~trial_id, ncol=2) +
    theme_bw() +
    theme(
      legend.position = 'top',
      legend.justification = 'left'
    )
  
  ggsave(r_tool, filename = file.path(plot_dir, 'scatters-tools', paste0(to, '_training_rescues_scatter.pdf')), width = 4, height = 24)
}
```
