---
title: "APM Manuscript Figures"
author: "Guillaume Kugener"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggrepel)
library(ggpubr)
library(ggridges)
library(ggimage)
library(grid)
library(jpeg)
```

```{r}
gt_dataset_dir <- '~/Documents/USC/USC_docs/ml/datasets/fps-1-uncropped/'
```

```{r}
# Plotting function
plot_single_frame <- function(data, ex_frame, title='', dataset_dir='') {
  combined_single_frame_example <- data %>%
    filter(frame == ex_frame)
  
  ex_img <- readJPEG(file.path(dataset_dir, 'JPEGImages', ex_frame))
  img_size <- dim(ex_img)
  
  g <- rasterGrob(
    ex_img, 
    width=unit(1, 'npc'),
    height=unit(1, 'npc'),
    interpolate = FALSE)
  
  g1 <- ggplot(data = combined_single_frame_example, 
               aes(xmin=x1, xmax=x2, ymin=img_size[1] - y2, ymax=img_size[1] - y1)) +
    annotation_custom(g, -Inf, Inf, -Inf, Inf) +
    geom_rect(fill='transparent', color='red', size=0.5)  +
    geom_text(aes(x=x1, y=img_size[1] - y1, label=tool), hjust=0, vjust=0, color='white') +
    ggtitle(title) +
    scale_x_continuous(limits=c(0, img_size[2]), expand = c(0,0)) +
    scale_y_continuous(limits=c(0, img_size[1]), expand = c(0,0)) +
    # facet_wrap(~source) +
    theme(
      legend.position = 'none', 
      axis.ticks = element_blank(),
      axis.text = element_blank(),
      title = element_text(size=10)
      # legend.justification = 'left',
    )
  
  return(g1)
}
```

```{r}
outcomes <- read_tsv('~/Documents/USC/USC_docs/ml/surgical-training-project/data/carotid_outcomes/complete_data_set.tsv')

training_successes <- outcomes %>% filter(`Trial 1 Success` == 0, `Trial 2 Success` == 1) %$% SurveyID
pros <- outcomes %>% filter(`Trial 1 Success` == 1, `Trial 2 Success` == 1) %$% SurveyID

outcomes_relevant <- outcomes %>% 
  dplyr::select(
    SurveyID,
    Group, endolast12mo, cadaverlast12,
    `Trial 1 TTH`, `Trial 2 TTH`, `Trial 1 Success`, `Trial 2 Success`, 
    `Trial 1 EBL`=`trial 1 ebl`, `Trial 2 EBL`=`trial 2 ebl`) %>%
  gather(variable, value, -endolast12mo, -cadaverlast12, -Group, -SurveyID) %>%
  mutate(trial=stringr::str_extract(pattern='Trial [0-9]', string=variable)) %>%
  mutate(variable_name=gsub('.* ', '', variable)) %>%
  mutate(trial_id=paste0('S', SurveyID, 'T', stringr::str_extract(pattern='[0-9]', string=trial))) %>%
  dcast(trial_id + Group + endolast12mo + cadaverlast12 ~ variable_name, value.var='value')
```

# Figure 1

Figure 1: 2 panels, panel 1 a screengrab of like our OG Carotid slide deck master slide where theres a bunch of tools annotated. I have an image but its very low res. Panel 2 is the one which plots position (x,y) color coded by tool, showing a general clustering. Just one example of the clustering I think is useful information to demonstrate that this is interesting

```{r}
# Example frame with 4+ tools
gt_results <- read_csv('~/Documents/USC/USC_docs/ml/datasets/fps-1-uncropped/ImageSets/Main/retinanet_surgical_1fps_complete.csv',
  col_names = c('file', 'x1', 'y1', 'x2', 'y2', 'tool')) %>%
  mutate(short_file_name=gsub('.*/', '', file)) %>%
  mutate(trial_id=gsub('[a-z]?_.*', '', short_file_name)) %>%
  mutate(frame=as.numeric(stringr::str_extract(pattern='[0-9]+', string=gsub('.*_', '', short_file_name))))
```

```{r eval=FALSE}
# Look for frames
gt_results %>%
  filter(tool %in% c('suction', 'cottonoid', 'grasper', 'muscle')) %>%
  group_by(frame) %>%
  dplyr::summarise(count=n()) %>%
  filter(count > 3) %>%
  arrange(-count) %>%
  mutate(code=paste0('cp ', frame, ' ~/Downloads/good_examples/')) %>%
  dplyr::select(code) %>%
  write.table(.,file = '~/Documents/USC/USC_docs/ml/datasets/fps-1-uncropped/JPEGImages/move_good_images.sh', col.names = F,quote = F,row.names = F)
```

```{r}
# Example frame
# example_frame <- 'S302T1_frame_00000071.jpeg'
example_frame <- 'S304T2_frame_00000028.jpeg'

example_frame_plot <- plot_single_frame(
  data = gt_results %>% mutate(frame=short_file_name), 
  ex_frame = example_frame,
  dataset_dir = gt_dataset_dir
)

ggsave(
  example_frame_plot + xlab('') + ylab(''),
  filename = '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/example_frame.pdf',
  units = 'in', width = 10, height = 5.6)
```

```{r}
# "Clustering" for the tool use
trial_example <- '304'

clustering_plot_data <- gt_results %>%
  filter(trial_id %in% c(rescues_t1, rescues_t2)) %>%
  # filter(trial %in% paste0('S', trial_example, 'T', c(1,2))) %>%
  mutate(frame_int=as.numeric(gsub('\\.jpeg', '', gsub('.*_', '', frame)))) %>%
  mutate(xc=(x1+x2)/2, yc=(y1+y2)/2) %>%
  filter(!is.na(tool)) %>%
  filter(tool %in% c('suction', 'cottonoid', 'grasper', 'muscle'))

clustering_plot_data %>%
  filter(trial_id == 'S309T2') %>%
  arrange(tool)

for (t1 in rescues_t1) {
  plot_data_c <- clustering_plot_data %>% 
    filter(trial_id %in% c(t1, gsub('T1', 'T2', t1))) %>%
    arrange(frame)
  
  if (nrow(plot_data_c) == 0) {
    next()
  }
  
  g1 <- ggplot(plot_data_c, aes(xc, yc, color=tool)) +
    geom_point() +
    ggtitle(paste0('Participant: ', gsub('S|T[12]', '', t1))) +
    facet_wrap(~trial_id) +
    theme(legend.position = 'top', legend.justification = 'left')
  
  ggsave(
    g1, 
    filename = file.path(
      '~/Documents/USC/USC_docs/ml/surgical-training-project/analysis/apm-characterization/plots/fvs_density/', 
      paste0(gsub('S|T[12]', '', t1), '.pdf')), 
    units = 'in', width=6, height = 4)
}

```

Figure 2: I dont know how to best represent this i could use some input on a good visual representation of tool-usage metrics. I thought about the horizontal bar graphs you made before which doucment tool usage, but I wanted something to compare successful and unsuccessful trials

```{r}
# Suctions only
suctions_only <- gt_results %>%
  filter(tool=='muscle') %>%
  left_join(., outcomes_relevant, by='trial_id')

single_df_suction_plot_ready <- suctions_only %>%
  group_by(trial_id) %>%
  mutate(r=rank(frame))

ggplot(single_df_suction_plot_ready, aes(frame, r, color=Success, group=trial_id)) +
  geom_step() +
  xlim(c(0,120)) +
  ylim(c(0, 120))
```

Figure 3) 4 scatterplots (each its own panel). Total disappearances ~ EBL; Suction disappearances ~ ebl; grasper disappearances~ebl; cottonoid~EBL

```{r}

```

